Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-12-29 awipev-CO2.Rmd
added note
clean up and chnaged variable names
Read nutrient data

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- tibble(
  read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
) %>% 
  dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
                measure_date = dmy(measure_date, tz="UTC"),
                date = as.Date(datetime)) %>% 
  dplyr::rename(ph_s_sf = pH_s_seafet,
                ph_s_dur = pH_s_durafet,
                qflag_ph_s_sf = qflag_pH_s_seafet,
                qflag_ph_s_dur = qflag_pH_s_durafet)

@@

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
discrete_is_na$pco2_calc_fb <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)
```

```{r Combine discrete and continous data, echo=FALSE}
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

```{r air-sea CO2, echo=FALSE, message= FALSE, warning=FALSE}
# calculations as described by de Carlo et al. (2013)
# we consider that mole fraction in air = ppm TO CHECK
# By convention, a negative flux indicates fluxes directed from the atmosphere to the ocean, and a positive flux indicates fluxes directed from the ocean to the atmosphere.
d_all <- d_all %>%
  dplyr::mutate(delta_pco2 = pco2_corr - pco2_air, # ppm
                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
                k = k600 * (Sc/600)^-0.5, #cm/h
                alp = seacarb::K0(S=sal_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
                alp = alp * (seacarb::rho(S = sal_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
                f_air_sea = k * alp * delta_pco2 # mmol/(m2 h)
                )

>>>>

```{r read and prepare discrete AT+CT, echo=FALSE, warning=FALSE, message=FALSE}
d <- tibble(
  read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
) %>% 
  dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
                measure_date = dmy(measure_date, tz="UTC"),
                date = as.Date(datetime)) %>% 
  dplyr::rename(ph_s_sf = pH_s_seafet,
                ph_s_dur = pH_s_durafet,
                qflag_ph_s_sf = qflag_pH_s_seafet,
                qflag_ph_s_dur = qflag_pH_s_durafet)

@@

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
discrete_is_na$pco2_calc_fb <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)
```
```{r read and prepare nutrients, echo=FALSE, warning=FALSE, message=FALSE}
# File "Ferrybox nutrients 2014-2018.xlsx" provided by 
# Willem van de Poll <w.h.van.de.poll@rug.nl> on 2020-01-16
nuts <- readxl::read_excel(paste0(path, "fb_data/Ferrybox nutrients 2014-2018.xlsx"),
                           skip =1) %>% 
  drop_na(date) %>% 
  dplyr::mutate(dt = as.POSIXct(paste0(date, " 12:00:00"))) # assuming sampling time 12:00
nuts
```
```{r Combine discrete and continous data, echo=FALSE}
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

```{r air-sea CO2, echo=FALSE, message= FALSE, warning=FALSE}
# calculations as described by de Carlo et al. (2013)
# we consider that mole fraction in air = ppm TO CHECK
# By convention, a negative flux indicates fluxes directed from the atmosphere to the ocean, and a positive flux indicates fluxes directed from the ocean to the atmosphere.

##TO DO: check calculations by Miller et al. (2020); use formulation of Wanninkhof 2014?
d_all <- d_all %>%
  dplyr::mutate(delta_pco2 = pco2_corr - pco2_air, # ppm
                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
                k = k600 * (Sc/600)^-0.5, #cm/h
                alp = seacarb::K0(S=sal_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
                alp = alp * (seacarb::rho(S = sal_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
                f_air_sea = k * alp * delta_pco2 # mmol/(m2 h)
                )
